\modLP{Identification of} Biological Regulatory Networks from Process Hitting models

### 2014-09-23 parts-phage-lambda.tex
parts of the PH of phage lambda

\begin{example}
\begin{align*}
  \PHs &= \{ cI, cro, cII, N \} \\
  \PHl_{cI} &= \{ cI_0, cI_1, cI_2 \} &
  \PHl_{cro} &= \{ cro_0, cro_1, cro_2, cro_3 \} \\
  \PHl_{cII} &= \{ cII_0, cII_1 \} &
  \PHl_{N} &= \{ N_0, N_1 \} \\
\end{align*}
  % TODO : figure PH du modèle
\end{example}

\begin{example}
  The IG inference of \pref{pps:inference-IG} applied to the PH of \todo{ref}
  produces the IG given in \pref{fig:phage-lambda-ig}.
  This IG contains all edges included in the original model except the
  self-influence on $cI$ : $\GRNedgef{cI}{+}{2}{cI} \notin E$;
  this is due to the fact that an equivalent dynamics exists without this edge.
  \begin{figure}[t]
  \centering
  \scalebox{1.2}{
  \begin{tikzpicture}[grn]
    %\path[use as bounding box] (-1.3,-0.75) rectangle (3.5,1.5);
    \node[inner sep=0] (cI) at (0,2.5) {cI};
    \node[inner sep=0] (cro) at (2.5,2.5) {cro};
    \node[inner sep=0] (cII) at (0,0) {cII};
    \node[inner sep=0] (N) at (2.5,0) {N};
    \path[->]
      (cI) edge[bend right] node[elabel, above=-4pt] {$-2$} (cro)
           edge[bend right] node[elabel, left=-2pt] {$-2$} (cII)
           edge[pos=.85] node[elabel, above=-2pt] {$-1$} (N)
      (cro) edge[bend right] node[elabel, above=-4pt] {$-1$} (cI)
            edge[loop right] node[elabel, below=-2pt] {$-3$} (cro)
            edge[pos=.65] node[elabel, below=-2pt] {$-3$} (cII)
            edge node[elabel, right=-4pt] {$-2$} (N)
      (cII) edge[bend right] node[elabel, left=-3pt] {$+1$} (cI)
      (N) edge node[elabel, above=-4pt] {$+1$} (cII);
  \end{tikzpicture}
  }
  \caption{\label{fig:phage-lambda-ig}
    Result of the IG inference performed on the PH of \todo{ref}.
  }
  \end{figure}
\end{example}

\begin{example}
  The parameters inference of \pref{pps:param_K} applied to the PH of \todo{ref}
  is conclusive for all parameters.
  The complete parametrization produced is available in \pref{tb:phage-lambda-k}.
  \begin{table}[t]
  \begin{align*}
    K_{cI, \emptyset} &= \{2\} &
    K_{cI, \{cro\}} &= \{0\} \\
    K_{cI, \{cII\}} &= \{2\} &
    K_{cI, \{cII;cro\}} &= \{2\} \\
    K_{N, \emptyset} &= \{1\} &
    K_{N, \{cro\}} &= \{0\} \\
    K_{N, \{cI\}} &= \{0\} &
    K_{N, \{cI;cro\}} &= \{0\} \\
    K_{cII, \emptyset} &= \{0\} &
    K_{cII, \{cro\}} &= \{0\} \\
    K_{cII, \{cI\}} &= \{0\} &
    K_{cII, \{cI;cro\}} &= \{0\} \\
    K_{cII, \{N\}} &= \{1\} &
    K_{cII, \{N;cro\}} &= \{0\} \\
    K_{cII, \{N;cI\}} &= \{0\} &
    K_{cII, \{N;cI;cro\}} &= \{0\} \\
    K_{cro, \emptyset} &= \{3\} &
    K_{cro, \{cro\}} &= \{2\} \\
    K_{cro, \{cI\}} &= \{0\} &
    K_{cro, \{cI;cro\}} &= \{2\}
  \end{align*}
  \caption{\label{tb:phage-lambda-k}
    Result of the parameters inference performed on the PH of \todo{ref}.
  }
  \end{table}
\end{example}

>>>>

\begin{example}
\begin{align*}
  \PHs &= \{ cI, cro, cII, N \} \\
  \PHl_{cI} &= \{ cI_0, cI_1, cI_2 \} &
  \PHl_{cro} &= \{ cro_0, cro_1, cro_2, cro_3 \} \\
  \PHl_{cII} &= \{ cII_0, cII_1 \} &
  \PHl_{N} &= \{ N_0, N_1 \} \\
\end{align*}

\begin{figure}[p]
\centering
\scalebox{1.3}{
\begin{tikzpicture}
  %\path[use as bounding box] (-4,-1.9) rectangle (4.5,3.9);

  % Sortes
  \TSort{(0,3.5)}{cI}{3}{l}
  \TSort{(0,-1.5)}{cro}{4}{l}
  \TSort{(7,1.5)}{N}{2}{r}

  % Sorte coopérative
  \TSetTick{cIcro}{0}{cI~$<$~1\\cro~$<$~2}
  \TSetTick{cIcro}{1}{cI~$<$~1\\cro~$\geq$~2}
  \TSetTick{cIcro}{2}{cI~$\geq$~1\\cro~$<$~2}
  \TSetTick{cIcro}{3}{cI~$\geq$~1\\cro~$\geq$~2}
  \TSort{(4,0.5)}{cIcro}{4}{r}

  % Actions de MàJ
  \THit{cI_1}{}{cIcro_0}{.west}{cIcro_2}
  \THit{cI_1}{}{cIcro_1}{.160}{cIcro_3}
  \THit{cI_2}{}{cIcro_0}{.west}{cIcro_2}
  \THit{cI_2}{}{cIcro_1}{.160}{cIcro_3}
  \path[bounce,bend left]
    \TBounce{cIcro_0}{}{cIcro_2}{.240}
    \TBounce{cIcro_1}{}{cIcro_3}{.south west} ;
  \THit{cI_0}{}{cIcro_2}{.160}{cIcro_0}
  \THit{cI_0}{}{cIcro_3}{.150}{cIcro_1}
  \path[bounce,bend right]
    \TBounce{cIcro_2}{}{cIcro_0}{.north west}
    \TBounce{cIcro_3}{}{cIcro_1}{.120} ;
  \THit{cro_2}{}{cIcro_0}{.210}{cIcro_1}
  \THit{cro_2}{}{cIcro_2}{.200}{cIcro_3}
  \THit{cro_3}{}{cIcro_0}{.210}{cIcro_1}
  \THit{cro_3}{}{cIcro_2}{.200}{cIcro_3}
  \path[bounce,bend left]
    \TBounce{cIcro_0}{}{cIcro_1}{.240}
    \TBounce{cIcro_2}{}{cIcro_3}{.south} ;
  \THit{cro_0}{}{cIcro_3}{.190}{cIcro_2}
  \THit{cro_0}{}{cIcro_1}{.200}{cIcro_0}
  \THit{cro_1}{}{cIcro_3}{.190}{cIcro_2}
  \THit{cro_1}{}{cIcro_1}{.200}{cIcro_0}
  \path[bounce,bend right]
    \TBounce{cIcro_1}{}{cIcro_0}{.north}
    \TBounce{cIcro_3}{}{cIcro_2}{.120} ;

  % Actions sortantes
  \THit{cIcro_3}{}{N_0}{.west}{N_1}
  \path[bounce,bend left] \TBounce{N_0}{}{N_1}{.south} ;
  \THit{cIcro_2}{}{N_1}{.west}{N_0}
  \path[bounce,bend right] \TBounce{N_1}{}{N_0}{.north} ;
\end{tikzpicture}
}
\caption{\label{fig:phage-lambda-cIcro-N}%
  A portion of the PH model used in this section modeling the phage lambda immunity response.
  This part of the whole model only depicts the interactions towards $N$ from components
  $cI$ and $cro$.
  The processes of the cooperative sort $cIcro$ are labeled by the configuration they represent.
}
\end{figure}

\begin{figure}[p]
\centering
\scalebox{1.3}{
\begin{tikzpicture}
  %\path[use as bounding box] (-4,-1.9) rectangle (4.5,3.9);

  % Sortes
  \TSort{(0,1)}{cI}{3}{l}
  \TSort{(4,0)}{cro}{4}{r}

  % Actions sortantes
  \THit{cro_3}{out=north east,in=south east,selfhit,min distance=50pt}{cro_3}{.south east}{cro_2}
    \path[bounce, bend left] \TBounce{cro_3}{}{cro_2}{.north east} ;

  \THit{cI_2}{}{cro_3}{.210}{cro_2}
    \path[bounce,bend right=40] \TBounce{cro_3}{}{cro_2}{.west} ;
  \THit{cI_2}{}{cro_2}{.210}{cro_1}
    \path[bounce,bend right=40] \TBounce{cro_2}{}{cro_1}{.west} ;
  \THit{cI_2}{}{cro_1}{.210}{cro_0}
    \path[bounce,bend right=40] \TBounce{cro_1}{}{cro_0}{.west} ;

  \THit{cI_1}{}{cro_0}{.110}{cro_1}
    \path[bounce,bend left] \TBounce{cro_0}{}{cro_1}{.south} ;
  \THit{cI_1}{}{cro_1}{.110}{cro_2}
    \path[bounce,bend left] \TBounce{cro_1}{}{cro_2}{.south} ;
  \THit{cI_1}{}{cro_2}{.110}{cro_3}
    \path[bounce,bend left] \TBounce{cro_2}{}{cro_3}{.south} ;

  \THit{cI_0}{}{cro_0}{.140}{cro_1}
    \path[bounce,bend left] \TBounce{cro_0}{}{cro_1}{.240} ;
  \THit{cI_0}{}{cro_1}{.140}{cro_2}
    \path[bounce,bend left] \TBounce{cro_1}{}{cro_2}{.240} ;
  \THit{cI_0}{}{cro_2}{.140}{cro_3}
    \path[bounce,bend left] \TBounce{cro_2}{}{cro_3}{.240} ;
\end{tikzpicture}
}
\caption{\label{fig:phage-lambda-cIcro-cro}%
  A portion of the PH model used in this section modeling the phage lambda immunity response.
  This part of the whole model only depicts the interactions towards $cro$ from components
  $cI$ and $cro$.
}
\end{figure}
\end{example}

\begin{example}
  The IG inference of \pref{pps:inference-IG} applied to the PH of \todo{ref}
  produces the IG given in \pref{fig:phage-lambda-ig}.
  This IG contains all edges included in the original model except the
  self-influence on $cI$ : $\GRNedgef{cI}{+}{2}{cI} \notin E$;
  this is due to the fact that an equivalent dynamics exists without this edge.
  \begin{figure}[t]
  \centering
  \scalebox{1.2}{
  \begin{tikzpicture}[grn]
    %\path[use as bounding box] (-1.3,-0.75) rectangle (3.5,1.5);
    \node[inner sep=0] (cI) at (0,2.5) {cI};
    \node[inner sep=0] (cro) at (2.5,2.5) {cro};
    \node[inner sep=0] (cII) at (0,0) {cII};
    \node[inner sep=0] (N) at (2.5,0) {N};
    \path[->]
      (cI) edge[bend right] node[elabel, above=-4pt] {$-2$} (cro)
           edge[bend right] node[elabel, left=-2pt] {$-2$} (cII)
           edge[pos=.85] node[elabel, above=-2pt] {$-1$} (N)
      (cro) edge[bend right] node[elabel, above=-4pt] {$-1$} (cI)
            edge[loop right] node[elabel, below=-2pt] {$-3$} (cro)
            edge[pos=.65] node[elabel, below=-2pt] {$-3$} (cII)
            edge node[elabel, right=-4pt] {$-2$} (N)
      (cII) edge[bend right] node[elabel, left=-3pt] {$+1$} (cI)
      (N) edge node[elabel, above=-4pt] {$+1$} (cII);
  \end{tikzpicture}
  }
  \caption{\label{fig:phage-lambda-ig}%
    Result of the IG inference performed on the PH of \todo{ref}.
  }
  \end{figure}
\end{example}

\begin{example}
  The parameters inference of \pref{pps:param_K} applied to the PH of \todo{ref}
  is conclusive for all parameters.
  The complete parametrization produced is available in \pref{tb:phage-lambda-k}.
  \begin{table}[t]
  \begin{align*}
    K_{cI, \emptyset} &= \{2\} &
    K_{cI, \{cro\}} &= \{0\} \\
    K_{cI, \{cII\}} &= \{2\} &
    K_{cI, \{cII;cro\}} &= \{2\} \\
    K_{N, \emptyset} &= \{1\} &
    K_{N, \{cro\}} &= \{0\} \\
    K_{N, \{cI\}} &= \{0\} &
    K_{N, \{cI;cro\}} &= \{0\} \\
    K_{cII, \emptyset} &= \{0\} &
    K_{cII, \{cro\}} &= \{0\} \\
    K_{cII, \{cI\}} &= \{0\} &
    K_{cII, \{cI;cro\}} &= \{0\} \\
    K_{cII, \{N\}} &= \{1\} &
    K_{cII, \{N;cro\}} &= \{0\} \\
    K_{cII, \{N;cI\}} &= \{0\} &
    K_{cII, \{N;cI;cro\}} &= \{0\} \\
    K_{cro, \emptyset} &= \{3\} &
    K_{cro, \{cro\}} &= \{2\} \\
    K_{cro, \{cI\}} &= \{0\} &
    K_{cro, \{cI;cro\}} &= \{2\}
  \end{align*}
  \caption{\label{tb:phage-lambda-k}%
    Result of the parameters inference performed on the PH of \todo{ref}.
  }
  \end{table}
\end{example}
